A Detection of the Environmental Dependence of the Stellar Profiles and Halos of Massive Central Galaxies

### 2017-07-12 draft/paper2.tex
Edit results 2

    When comparing \nbcg{} and \rbcg{} we will also always make sure that the two 
    samples are well matched both in terms of \mstar{} as well as in terms of redshift. 
    Please see the next section and Appendix~\ref{app:match} for more details.

@@

    We now ask whether or not galaxies from our sample have \mden{} profiles that 
    depend on \mhalo{} (at fixed \mstar{}). 
    For this, we will build matched samples drawing from \rbcg{} and \nbcg{} that are 
    carefully matched in \mstar{} and redshift using a KDTree algorithm 
    (see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
    By matching the redshift distributions within $0.3 < z < 0.5$, we ensure that the 
    \mden{} profiles from both samples are impacted by seeing and background subtraction 
    at similar levels. 
    To match the two samples by stellar mass, we will use two different methods:

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the profiles of galaxies at fixed \mtot{} and at fixed 
    \minn{} for our two matched samples, and shows the main results of this paper which 
    is that we find a clear halo mass dependence in the \mden{} profiles of massive 
    galaxies. 
    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the two 
    profiles, $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
    \log(\mu_{\star, \mathrm{cenLowMh}})$, 
    with errors computed via bootstrap resampling. 
    In Appendix~\ref{app:robust}, we present a variety of tests that verify the 
    robustness of these results against different uncertainties.

    There are several important points to be noticed in Fig~\ref{fig:prof_1}. 
    First, when galaxies are matched by \mtot{}, although we detect a robust 
    environmental dependence, it mainly only becomes prominent in the outskirts 
    at $R>50$ kpc. 
    This partially explains the difficulties for previous works to detect this effect
    on shallower images. 
    Second, we find that central galaxies in more massive dark mater halos display 
    more flattened inner profile and more significant outer stellar envelope than 
    the ones living in less massive halos. 
    Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each other 
    at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for ETGs at this \mtot{}. 
    Finally, such systematic difference in structure may become more significant 
    at very high-mass end. 
    We see evidence of this effect when we compare the $Delta$ profiles in two \mtot{} 
    bins (see Fig~\ref{fig:prof_2} and discussion in 
    Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes somewhat
    incomplete} and when we discuss the relation between \mtot{} and \minn{} for 
    these two samples (see Fig~\ref{fig:scaling_relation}). 
    This potential interesting result and its implication is worth more investigations 
    later.

    Meanwhile, the subtle environmental dependence of \mden{} profiles for the 
    \mtot{}-matched samples suggests that environment does not play the major role in 
    shaping massive galaxies \textbf{at fixed total stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the in-situ component}, how does environment affect their 
    subsequent mass assembly?
    Assuming that the \minn{} is reasonable proxy of in-situ mass, we look into this 
    question by comparing the \mden{} profiles of the \minn{}-matched samples ( 
    Fig~\ref{fig:prof_1}, right).  
    Although the median \mden{} profiles are similar at $r \leq 10$ kpc, the
    central galaxies in more massive halos clearly possess much more prominent outer
    envelope. 
    This result is robust in a series of statistical and systematical tests 
    (see Appendix~\ref{app:robust}.

    At the same time, the uniform slope of the \mden{} profiles within 
    10 kpc is in sharp contrast with the large scatter of the outskirts. 
    It hints that these two regions are shaped by distinctive processes, and may 
    explain their differences in environmental dependency. 
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The stochastic nature of the merging process also helps explain the 
    large scatter in the distributions of outer \mden{} profiles. 
    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
    we show the 3-color images of randomly selected massive central galaxies that 
    have similar \minn{} 
    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.

>>>>

@@

    First, we ask whether the \mden{} profiles of massive central galaxies show 
    \mhalo{}-dependence within 100 kpc at fixed \mstar{}. 
    To perform meaning comparison, we build matched samples drawing from \rbcg{} and 
    \nbcg{} that are carefully matched in \mstar{} and redshift using KDTree algorithm 
    (please see Appendix~\ref{app:match} and Fig~\ref{fig:match} for details). 
    The similar distributions of redshift of the matched samples ensure that the 
    median \mden{} profiles from both samples are affected by seeing and background 
    subtraction to the same extend. 
    We address this issue more in Appendix~\ref{app:redshift}.

    We match the \rbcg{} and \nbcg{} samples using both \mtot{} and \minn{} in this
    work. 
    As explained in Paper~1, we use \mtot{} as proxy of the ``total'' \mstar{}
    of massive galaxies while treat \minn{} as a rough indicator of the mass of the 
    \textit{in-situ} component.

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
    in \rbcg{} (orange-red color) and \nbcg{} (grey-black color) at fixed \mtot{} 
    (left panel) and at fixed \minn{} (right panel). 
    The top panels show the individual \mden{} profiles along with the median profiles 
    for both samples. 
    The bottom panel of Fig~\ref{fig:prof_1} shows the difference between the median 
    \mden{} profile of \rbcg{} and \nbcg{} samples, with errors computed via bootstrap 
    resampling.
    $\Delta = \log(\mu_{\star, \mathrm{cenHighMh}}) - 
    \log(\mu_{\star, \mathrm{cenLowMh}})$. 
    This figure presents the main results of this work: \textbf{The \mden{} profiles of 
    massive central galaxies show \mhalo{}-dependence at both fixed \mtot{} and 
    \minn{}.}
    For both \mtot{}-- and \minn{}--matched samples, we see systematic differences
    between the median \mden{} profile of \rbcg{} galaxies and the one for \nbcg{}
    galaxies.

    We perform statistical tests to show that the differences we see in the median 
    \mden{} profiles are significant. 
    We also conduct a variety of tests that verify the robustness of these results 
    against choices of \mtot{} bins, $\lambda$ cut, and redshift range. 
    Please see Appendix~\ref{app:robust} for more details about these tests.

    There are several important points to be noticed on the left panel of 
    Fig~\ref{fig:prof_1}.

        \item First, for the \mtot{} matched sample, although the difference in 
            median \mden{} profiles is systematical and robust, the overall difference 
            is very subtle and only becomes clear in the outskirts at $R>50$ kpc, 
            which explains why such environment dependence is extremely difficult 
            for previous works to detect using shallower images.

        \item Second, we find that, at fixed \mtot{}, massive central galaxies in 
            more massive dark mater halos display shallower \mden{} profiles that the 
            ones living in less massive haloes. 
            This can be seen from the more flattened inner \mden{} profile and more 
            significant outer stellar halos.

        \item Third, the median \mden{} profiles of \rbcg{} and \nbcg{} cross each 
            other at ${\sim} 15$-20 kpc, the expected $R_{\mathrm{e}}$ for massive 
            ETGs around this \mtot{}.

        \item Finally, such systematic difference in \mden{} profiles may become more 
            significant at higher \mtot{}.
            We see evidence of this using the $Delta$ profiles of two \mtot{} 
            bins (see Fig~\ref{fig:prof_2} and discussion in 
            Appendix~\ref{app:robust})\footnote{Though the lower \mtot{} bin becomes 
            somewhat incomplete} and when we discuss the relation between \mtot{} and 
            \minn{} (see Fig~\ref{fig:scaling_relation}). 
            This trend has potentially interesting implication that is worth more 
            investigations later.

    Generally speaking, such subtle environmental dependence of \mden{} profiles in 
    the \mtot{}-matched samples suggests that environment does not play a major role 
    in shaping massive galaxies \textbf{at fixed ``total'' stellar mass}.
    Therefore it is interesting to ask, for massive galaxies that \textbf{contain 
    similar \mstar{} in the \textit{in-situ} component}, how does environment affect 
    their subsequent mass assembly?
    Assuming \minn{} is reasonable tracer of the ``in-situ'' mass, we compare the 
    \mden{} profiles of \minn{}-matched samples (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive halos host much more prominent outer 
    stellar halo.

    Meanwhile, the uniform slope of the \mden{} profile within 10 kpc is in sharp 
    contrast with the large \textit{intrinsic} scatter in the outskirts. 
    It hints that these two regions are shaped by distinctive processes, and may 
    explain why they depend on environment at different levels.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The stochastic nature of the merging process also helps explain the 
    large scatter in the distributions of outer \mden{} profiles. 
    We illustrate this interesting diversity in Fig~\ref{fig:m100_m10_color}, where 
    we show the 3-color images of randomly selected massive central galaxies that 
    have similar \minn{} 
    ($11.1 \leq \log (M_{\star,\ 10\mathrm{kpc}}/M_{\odot}) < 11.2$)
    but different \mtot{}.   
    From the top-left to the bottom-right, the \mtot{} of these galaxies increases
    from $10^{11.22} M_{\odot}$ to $10^{11.75} M_{\odot}$.
